---
title: "models"
author: "Alex Liu"
date: "2023-04-03"
output: 
  html_document:
    code-folding: hide
---

```{r message = F, warning = F}
library(EBImage)
library(tidyverse)
library(pracma)
library(randomForest)
library(ggimage)
```

# Random Forest (Pixel-Based)

```{r}
labels = list.files("../bio_data/Biotechnology/data_processed/cell_images/")
cell_boundaries_raw = read.csv("../bio_data/Biotechnology/data_processed/cell_boundaries.csv.gz")

cluster_ids = list()

for (i in 1:length(labels)) {
  
  cluster_file = list.files(paste0("../bio_data/Biotechnology/data_processed/cell_images/", labels[i]))
  
  cluster_ids[i] <- list(gsub(".*cell_|.png", "", cluster_file))
}

cluster_imgs = list()

for (i in 1:length(labels)) {
  
  cluster_file = list.files(paste0("../bio_data/Biotechnology/data_processed/cell_images/", labels[i]), full.names=T)
  
  cluster_imgs[i] <- list(sapply(cluster_file, readImage, simplify = F))

}
```

```{r}
get_inside = function(cellID, img, cell_boundaries) {
  
  cell_boundary = cell_boundaries |>
    filter(cell_id %in% cellID)
  
  # rescale the boundary according to the pixels
  pixels = dim(img)
  cell_boundary$vertex_x_scaled <- 1+((cell_boundary$vertex_x - min(cell_boundary$vertex_x))/0.2125)
  cell_boundary$vertex_y_scaled <- 1+((cell_boundary$vertex_y - min(cell_boundary$vertex_y))/0.2125)
  
  # identify which pixels are inside or outside of the cell segment using inpolygon
  pixel_locations = expand.grid(seq_len(nrow(img)), seq_len(ncol(img)))
  
  pixels_inside = inpolygon(x = pixel_locations[,1],
                            y = pixel_locations[,2],
                            xp = cell_boundary$vertex_x_scaled,
                            yp = cell_boundary$vertex_y_scaled,
                            boundary = TRUE)
  
  img_inside = img
  img_inside@.Data <- matrix(pixels_inside, nrow = nrow(img), ncol = ncol(img))
  
  return(img_inside)
}

mask_resize = function(img, img_inside, w = 50, h = 50) {
  
  img_mask = img*img_inside
  
  # then, transform the masked image to the same number of pixels, 50x50
  img_mask_resized = resize(img_mask, w, h)
  
  return(img_mask_resized)
}
```

```{r}
cluster_imgs_masked_resized = list()

for (i in 1:length(labels)) {
  cell_boundaries = cell_boundaries_raw |>
    filter(cell_id %in% cluster_ids[[i]])
    
  cluster_imgs_inside <- mapply(get_inside, cluster_ids[[i]], cluster_imgs[[i]], MoreArgs = list(cell_boundaries = cell_boundaries), SIMPLIFY = FALSE)
  
  cluster_imgs_masked_resized[i] = list(mapply(mask_resize, cluster_imgs[[i]], cluster_imgs_inside, SIMPLIFY = FALSE))

}
```

```{r}
set.seed(6)

times = c()

for (i in 1:length(labels)) {
  times[i] = length(cluster_ids[[i]])
}

y = factor(rep(labels, times = times))
x = cbind(do.call(cbind, lapply(cluster_imgs_masked_resized[[1]],c)),
          do.call(cbind, lapply(cluster_imgs_masked_resized[[2]],c)))

for (i in 3:length(cluster_imgs_masked_resized)) {
  x = cbind(do.call(cbind, lapply(cluster_imgs_masked_resized[[i]], c)),
            x)
}

rf = randomForest(x = t(x), y = y)
rf
```

```{r}
importance_img = Image(data = matrix(rf$importance, 50, 50))
display(importance_img/quantile(importance_img, 0.99), method = "raster")
```

Cluster 1 and 2 have the lowest error rate with , while other clusters are almost all misclassified.

Possible Reasons for high error rate:

1. Inconsistent file size for different clusters.
2. Model not complex enough to capture more complex shapes.
3. Pixel intensities not normalised.
4. Cells not aligned with each other.

## Extracted features with cell boundary
```{r}
set.seed(66)
cluster_img_features = list()
xf = c()

for (i in 1:length(labels)) {
  cell_boundaries = cell_boundaries_raw |>
    filter(cell_id %in% cluster_ids[[i]])
    
  cluster_imgs_inside <- mapply(get_inside, cluster_ids[[i]], cluster_imgs[[i]], MoreArgs = list(cell_boundaries = cell_boundaries), SIMPLIFY = FALSE)
  
  cluster_img_features[i] <- list(mapply(computeFeatures,
                                x = cluster_imgs_inside,
                                ref = cluster_imgs[[i]],
                                MoreArgs = list(expandRef = NULL)))
  
  xf <- cbind(cluster_img_features[[i]], xf)
  
}

rff = randomForest(x = t(xf), y = y)
rff
```

There is a very small improvement in error rate.

```{r}
images = c()
for (i in 1:length(labels)) {
  
  cluster_file = list.files(paste0("../bio_data/Biotechnology/data_processed/cell_images/", labels[i]), full.names = T)
  
  images <- append(images, cluster_file)
}

pc = princomp(t(xf), cor = T)

features_pc_df = data.frame(PC1 = pc$scores[, 1],
                            PC2 = pc$scores[, 2],
                            cluster = y,
                            images = images)

ggplot(features_pc_df, aes(x = PC1, y = PC2)) + 
  geom_point(aes(colour = cluster)) +
  geom_image(aes(image = images), size=0.03)
```

Despite the high error% of the random forest model, there is still a noticeable distance between high and low intensity images. 

```{r}
ggplot(features_pc_df, aes(x = PC1, y = PC2)) + 
  geom_point(aes(colour = cluster))
```

However, it may be difficult to use PCA loading to interpret the extracted features associated with the visual characteristics.

## Is there a difference for Random Forest without the use of cell boundary

```{r}
set.seed(61)
xnobound = c()

for (i in 1:length(cluster_imgs)) {
  xnobound = cbind(do.call(cbind, lapply(cluster_imgs_masked_resized[[i]], c)),
            xnobound)
}

rf = randomForest(x = t(xnobound), y = y)
rf
```

```{r}
importance_img = Image(data = matrix(rf$importance, 50, 50))
display(importance_img/quantile(importance_img, 0.99), method = "raster")
```


Slight improvement but not significant, with improvement of about 2%. Cluster 1 and 2 remains the clusters with lowest error rate.

### Same random forest with extracted features

```{r}
set.seed(62)
cluster_img_features_nobound = list()
xfnobound = c()

for (i in 1:length(labels)) {
  cell_boundaries = cell_boundaries_raw |>
    filter(cell_id %in% cluster_ids[[i]])
  
  cluster_img_features[i] <- list(mapply(computeFeatures,
                                x = cluster_imgs[[i]],
                                ref = cluster_imgs[[i]],
                                MoreArgs = list(expandRef = NULL)))
  
  xfnobound <- cbind(cluster_img_features[[i]], xfnobound)
  
}

rff = randomForest(x = t(xfnobound), y = y)
rff

```

Similar error rate. It did get better at identifying images in clusters 1 and 2, however, it came at the expense of identifying other clusters. 


